Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-07 paper.tex
update

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers. One is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction of web services enables us to pair service functionalities through understanding and reasoning those semantic descriptions. Optimisation problems are another challenge. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS. This paper develops a more applicable way for measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
\end{abstract}

@@

The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}. Particularly, this paper considers the quality of semantic matchmaking quality and QoS and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation (PSO). We aim to provide a more applicable and adaptive way to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

@@

The remains of this paper are organised as the following: Sect. \ref{background} provides the background on the semantic web service composition, and related works; Sect. \ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents and analyses the experiment; Sect. \ref{conclusion} concludes our work.

@@

However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology. Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method. In QoS, only cost and time are considered in the optimised problems. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

@@

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as particles in their PSO algorithm considering QoS optimisation. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as different particle representations from \cite{da2016particle}.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found concretely to meet $Comp.G$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O). To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

@@

\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. Overall, this approach is different from \cite{da2016particle}, as we use weighted graphs as particle presentation while considering a comprehensive quality.

\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.

@@

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the semantic matchmaking quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, which is a taxonomy-based measurement for ontology matching. This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services. Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as the quality of the semantic link in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

Further more, edges represent services connections in our weighted graph presentations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations. The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the mean value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level. where $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which can be described in the Fig. \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively on the construct level. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined previously.

@@

\begin{equation}
\label{equation6}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation7}
\hat{Q_i} = 
\begin{cases}
	\frac{Q_i - Q_{i, min}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $i$ $=$ $1$, $2$, $3$, and $4$ with $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation8}
\hat{Q_i} = 
\begin{cases}
	\frac{Q_{i,max} - \hat{Q_i}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $i$ $=$ $1$, and $2$ with $Q_1$ as $T$ and $Q_2$ as $C$.

@@

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a evaluation. WSC09 provides problems where five tasks consisted in with variable size in both services, and ontologies. Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

@@

First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1 \hat{A} + w_2R + w_3(1 - T) + w_4(1 - C)$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and its $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach. We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those of QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively. However, the mean value $Q_{QoS}$ at optimum at 100th generation of QoS-aware approach can obtain a slightly higher value than that of our approach. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

@@

Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in two composition weighted graphs representations under two different methods. The Fig. \ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method. Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different part. Therefore, we make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertex in terms of quality of semantic matchmaking and QoS attributes. We also look at $\Delta Q$ which reveals the amount of variation between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off. There is an consistency in our methods that edges are with higher values and service vertex with slightly lower QoS. To demonstrate the benefits of the positive value, we analyse the smallest value $e_4$ and demonstrate how the output and required input are different in in Fig. \ref{comparisontaxonomy}. $Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to $Con103314376$ and $Con2037585750$ respectively under two methods while $Inst658772240$ are the required input related to $Con2113572083$, in which there exist $Con103314376$ $\sqsubseteq_{2}$ $Con2113572083$ and $Con2037585750$ $\sqsubseteq_{3}$ $Con2113572083$. It is obviously that our approach select the service providing parameters that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=6cm]{comparision.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparison}
\end{figure}
\vspace{0.3cm}
\begin{figure}
\centerline{
\fbox{
\includegraphics[width=4cm]{comparisontaxonomy.pdf}}}
 \caption{Example Comparison of Edge 4 in Task 3 solution under two methods.}
 \label{comparison}
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Comparison of Composition Weighted Graphs}
\label{comparisontaxonomy}
\begin{tabular}{l|l|l|l|l}
\hline
\multicolumn{2}{l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
                    & $q(e_{s})$   &1        &1                       &0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
\multicolumn{2}{l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers. One is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction of web services enables us to pair service functionalities through understanding and reasoning those semantic descriptions. Optimisation problems are another challenge. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS. This paper develops a more applicable way of measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
\end{abstract}

@@

The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}. Particularly, this paper considers the quality of semantic matchmaking quality and QoS and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation (PSO). We aim to provide a more applicable way to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

@@

The remains of this paper are organised as the following: Sect. \ref{relatedWork} provides related works in the semantic web service composition; Sect. \ref{qswsc_approach} presents an overview of comprehensive quality-aware semantic automated web service composition consisting of comprehensive quality evaluation model, proposed weighted graphs as solution presention and PSO-based service composition algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents and analyses the experiment; Sect. \ref{conclusion} concludes our work.

@@

However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most semantic web services applications, as it takes unpredictable cost and time for the domain experts to establish required ontology. Additionally, a semi-automated service composition approach is considered in their paper, rather than a fully automated method. Only cost and time are considered in the optimised problems. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

@@

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as particles in their PSO algorithm considering QoS optimisation. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising weighed graphs as a different semantic web service composition representations from \cite{da2016particle}.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set. It typically refers to users' functional requirement. Another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from a Service Repository: $S =  \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. If no atomic web service could satisfy the composite goal, a combination of web services will be found to meet $Comp.G$. To ensure the composite solution returns the desired $Comp.G$, we consider a comprehensive quality model for service discovery and selection, where challenges $(1)$ and $(2)$ mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional requests. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Taxonomy\}$. A web service matching process is to match the output and input concepts of two services according to the Taxonomy within an Ontology (O). To measure the quality of semantic matchmaking, different matching levels are typically considered in the literature \cite{paolucci2002semantic}. To understand these levels, let us define two web services associated with concept-related parameters in a particular domain. $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S_{2}$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$. The matching levels to be considered are:

@@

\section{Comprehensive quality-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. A functional requirement is defined as $F(T_{Input}, T_{Output})$ , and a nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered as graph vertices while edges are assigned with semantic matchmaking quality as weights. Step 4,5: The selection of web services performs PSO algorithm in Sect. \ref{pso_algorithm} to find best particle location. This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation while considering a comprehensive quality for optimisation problem.

\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect. \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the mode model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfies the quality of QoS with considering its functional quality.

@@

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, match types are considered to be one factor for the semantic matchmaking quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy-based measurement for ontology matching. This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services. Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {matchType})$ is set up as the same as that in \cite{lecue2009optimizing} as 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

Further more, edges represent services connections in our weighted graph presentations, where assigned weight value $q(e_{sm})$ is considered to be semantic matching quality on edge level according to parameter aggregations. The weight value $q(e_{sm})$ is defined in \ref{equation3}, where $q(e_ {matchType})$ and $q(e_ {similarity})$ are the average value of concept-related parameters quality in $q(p_{mt})$ and $q(p_{s})$ respectively.

@@

\subsection{Composition Weighted Graph}
We defined our semantic web service composition solution as $WG = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of edges $E = {e_{1}, e_{2},... e_{n}}$. Each $e$ is associated with $q(e_{sm})$ as weight value that mapped to a pair of quality values $q(e_{mt})$ and $q(e_{s})$ on the edge level, and $e_{m}$ is expressed as $(S_{a},S_{b})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition, which is described in the Fig. \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$ assigned as weights.

@@

\begin{equation}
\label{equation6}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation7}
\hat{Q_i} = 
\begin{cases}
	\frac{Q_i - Q_{i, min}}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $i$ $=$ $1$, $2$, $3$, and $4$ with $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation8}
\hat{Q_i} = 
\begin{cases}
	\frac{Q_{i,max} - Q_i}{Q_{i, max} - Q_{i, min}} & \text{ if }Q_{i, max} - Q_{i, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $i$ $=$ $1$, and $2$ with $Q_1$ as $T$ and $Q_2$ as $C$.

@@

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a evaluation. WSC09 provides problems where five tasks consisted in with variable size in both services, and ontologies. Therefore, it is a proper dataset for the scalability measures for our quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

@@

First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach. We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively. Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

@@

Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in two composition weighted graphs representations under two different methods. The Fig. \ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different. Therefore, we make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertex in terms of quality of semantic matchmaking and QoS attributes. We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off. To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in in Fig. \ref{comparisontaxonomy}. $Ser1640238160$ and $Ser1947554374$ are selected service vertex with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to $Con103314376$ and $Con2037585750$ respectively while $Inst658772240$ are the required input related to $Con2113572083$, in which there exist $Con103314376$ $\sqsubseteq_{2}$ $Con2113572083$ and $Con2037585750$ $\sqsubseteq_{3}$ $Con2113572083$. It is obviously that our approach select the service providing $Inst795998200$ that are closer the users' requirement, which means our methods results in better semantic matchmaking quality.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=6cm]{comparision.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparison}
\end{figure}
\vspace{0.3cm}
\begin{figure}
\centerline{
\fbox{
\includegraphics[width=4cm]{comparisontaxonomy.pdf}}}
 \caption{Example Comparison of Edge 4 in Task 3 solution under two methods.}
 \label{comparisontaxonomy}
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Comparison of Composition Weighted Graphs}
\label{comparisontaxonomy}
\begin{tabular}{l|l|l|l|l}
\hline
\multicolumn{2}{l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
                    & $q(e_{s})$   &1        &1                       &0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
\multicolumn{2}{l|}{WG QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
\end{tabular}
\end{table}
